Generalized Derivation for the motion of an n-pendulum system

### 2021-05-07 paper/paper.tex
math

% @Author: UnsignedByte
% @Date:   11:12:32, 08-Dec-2020
% @Last Modified by:   UnsignedByte
% @Last Modified time: 2021-05-06 23:13:10

@@

First, we try to solve for $\frac{\partial L}{\partial \dot \theta_i}$ by taking a derivative of $L$ with respect to $\dot\theta_i$. We first make an important observation: all terms in multiple sums of $L$ that do not contain $\dot\theta_i$ can be treated as a constant, and will be removed. We immediately can remove $V,$ which leaves us with the $T$ term. Because $\dot\theta_i$ appears if and only if $j=i$ or $k=i$, we can simplify our equation much further. We can arbitrarily plug in $j=i$ or $k=i$ into our equation. Before this, however, we must separate our sum due to the special case $i=i$. Firstly, the term simplifies to $\dot\theta_i^2$ when $i=i,$ which cannot be differentiated while treating one of the $\dot\theta_i$ as a constant. It is also the only term that would be double counted if we had kept the simple single sum and doubled it. This gives us 3 cases, one for $i=i,$ one for $1\leq k\le i$ and finally for $i+1\leq k \leq n$. The latter two are counted twice, once as $\dot\theta_i\dot\theta_k$ and once as $\dot\theta_k\dot\theta_i,$ thus we need a factor of two before both sums. This gives us the following, which we can further simplify:
\begin{align*}
&\frac{ml^2}{2}\frac{\partial L}{\partial \dot \theta_i}\left((n-i+1)\dot\theta_i^2 + 2\sum_{k=1}^{i-1}(n-i+1)\dot\theta_i\dot\theta_k\cos(\theta_i-\theta_k)\right.\\
&\qquad\qquad+ \left.2\sum_{k=i+1}^n(n-k+1)\dot\theta_i\dot\theta_k\cos(\theta_i-\theta_k)\right)\\
&= ml^2\left((n-i+1)\dot\theta_i + (n-i+1)\sum_{k=1}^{i-1}\dot\theta_k\cos(\theta_i-\theta_k)\right.\\
&\qquad\qquad+ \left.\sum_{k=i+1}^n(n-k+1)\dot\theta_k\cos(\theta_i-\theta_k)\right)
\end{align*}
Next we take the derivative with respect to time:
\begin{align*}
&= ml^2\frac{d}{dt}\left((n-i+1)\dot\theta_i + (n-i+1)\sum_{k=1}^{i-1}\dot\theta_k\cos(\theta_i-\theta_k)\right.\\
&\qquad\qquad+ \left.\sum_{k=i+1}^n(n-k+1)\dot\theta_k\cos(\theta_i-\theta_k)\right)\\
&= ml^2\left((n-i+1)\ddot\theta_i + (n-i+1)\sum_{k=1}^{i-1}\left(\ddot\theta_k\cos(\theta_i-\theta_k)-\dot\theta_k(\dot\theta_i-\dot\theta_k)\sin(\theta_i-\theta_k)\right)\right.\\
&\qquad\qquad+ \left.\sum_{k=i+1}^n(n-k+1)\left(\ddot\theta_k\cos(\theta_i-\theta_k)-\dot\theta_k(\dot\theta_i-\dot\theta_k)\sin(\theta_i-\theta_k)\right)\right)\\
\end{align*}
\subsection{Generalization to an Infinite Rope}
e
\end{document}

>>>>

% @Author: UnsignedByte
% @Date:   11:12:32, 08-Dec-2020
% @Last Modified by:   UnsignedByte
% @Last Modified time: 2021-05-07 00:29:29

@@

First, we try to solve for $\frac{\partial L}{\partial \dot \theta_i}$ by taking a derivative of $L$ with respect to $\dot\theta_i$. We first make an important observation: all terms in multiple sums of $L$ that do not contain $\dot\theta_i$ can be treated as a constant, and will be removed. We immediately can remove $V,$ which leaves us with the $T$ term. Because $\dot\theta_i$ appears if and only if $j=i$ or $k=i$, we can simplify our equation much further. We can arbitrarily plug in $j=i$ or $k=i$ into our equation. Before this, however, we must separate our sum due to the special case $i=i$. Firstly, the term simplifies to $\dot\theta_i^2$ when $i=i,$ which cannot be differentiated while treating one of the $\dot\theta_i$ as a constant. It is also the only term that would be double counted if we had kept the simple single sum and doubled it. This gives us 3 cases, one for $i=i,$ one for $1\leq k\le i$ and finally for $i+1\leq k \leq n$. The latter two are counted twice, once as $\dot\theta_i\dot\theta_k$ and once as $\dot\theta_k\dot\theta_i,$ thus we need a factor of two before both sums. This gives us the following, which we can further simplify:
\begin{align*}
&\frac{ml^2}{2}\frac{\partial L}{\partial \dot \theta_i}\left((n-i+1)\dot\theta_i^2 + 2\sum_{k=1}^{i-1}(n-i+1)\dot\theta_i\dot\theta_k\cos(\theta_i-\theta_k)\right.\\
&\qquad\qquad+ \left.2\sum_{k=i+1}^n(n-k+1)\dot\theta_i\dot\theta_k\cos(\theta_i-\theta_k)\right)\\
&= ml^2\left((n-i+1)\dot\theta_i + (n-i+1)\sum_{k=1}^{i-1}\dot\theta_k\cos(\theta_i-\theta_k)\right.\\
&\qquad\qquad+ \left.\sum_{k=i+1}^n(n-k+1)\dot\theta_k\cos(\theta_i-\theta_k)\right)
\end{align*}
Next we take the derivative with respect to time:
\begin{align*}
&= ml^2\frac{d}{dt}\left((n-i+1)\dot\theta_i + (n-i+1)\sum_{k=1}^{i-1}\dot\theta_k\cos(\theta_i-\theta_k)\right.\\
&\qquad\qquad+ \left.\sum_{k=i+1}^n(n-k+1)\dot\theta_k\cos(\theta_i-\theta_k)\right)\\
&= ml^2\left((n-i+1)\ddot\theta_i + (n-i+1)\sum_{k=1}^{i-1}\left(\ddot\theta_k\cos(\theta_i-\theta_k)-\dot\theta_k(\dot\theta_i-\dot\theta_k)\sin(\theta_i-\theta_k)\right)\right.\\
&\qquad\qquad+ \left.\sum_{k=i+1}^n(n-k+1)\left(\ddot\theta_k\cos(\theta_i-\theta_k)-\dot\theta_k(\dot\theta_i-\dot\theta_k)\sin(\theta_i-\theta_k)\right)\right)\\
\end{align*}
Now that we have the $\frac{d}{dt}\left(\frac{\partial L}{\partial \dot\theta_i}\right)$ term, we want to get $\frac{\partial L}{\partial \theta_i}$ in order to finish our Lagrangian equations. We approach this with the same method: simplifying our equation for $L$ with only the terms consisting of $\theta_i$. For $T$, we have the same situation: a term only contains $\theta_i$ when $j=i$ or $k=i$. This gives us a similar equation, but one where $\dot\theta_i^2$ can be removed. This time, however, we must also consider $V$. $V$ is easy to simplify: the only term with $\theta_i$ is simply the $ith$ term of the sum. This gives us the following equation:
\begin{align*}
&\frac{ml^2}{2}\frac{\partial L}{\partial \theta_i}\left(2\sum_{k=1}^{i-1}(n-i+1)\dot\theta_i\dot\theta_k\cos(\theta_i-\theta_k)\right.\\
&\qquad\qquad+ \left.2\sum_{k=i+1}^n(n-k+1)\dot\theta_i\dot\theta_k\cos(\theta_i-\theta_k)\right)\\
&\qquad\qquad+ \frac{\partial L}{\partial \theta_i}\left(mgl(n-i+1)\cos\theta_i\right)\\
&=-ml^2\left(\sum_{k=1}^{i-1}(n-i+1)\dot\theta_i\dot\theta_k\sin(\theta_i-\theta_k)\right.\\
&\qquad\qquad+ \left.\sum_{k=i+1}^n(n-k+1)\dot\theta_i\dot\theta_k\sin(\theta_i-\theta_k)\right)\\
&\qquad\qquad- mgl(n-i+1)\sin\theta_i\\
\end{align*}

Plugging all of this into Lagrange's equations gives and simplifying, we get our final equation.
\begin{align*}
0&=ml^2\left((n-i+1)\ddot\theta_i + (n-i+1)\sum_{k=1}^{i-1}\left(\ddot\theta_k\cos(\theta_i-\theta_k)-\dot\theta_k(\dot\theta_i-\dot\theta_k)\sin(\theta_i-\theta_k)\right)\right.\\
&\qquad\qquad+ \left.\sum_{k=i+1}^n(n-k+1)\left(\ddot\theta_k\cos(\theta_i-\theta_k)-\dot\theta_k(\dot\theta_i-\dot\theta_k)\sin(\theta_i-\theta_k)\right)\right)\\
&\qquad\qquad+ml^2\left(\sum_{k=1}^{i-1}(n-i+1)\dot\theta_i\dot\theta_k\sin(\theta_i-\theta_k) + \sum_{k=i+1}^n(n-k+1)\dot\theta_i\dot\theta_k\sin(\theta_i-\theta_k)\right)\\
&\qquad\qquad+ mgl(n-i+1)\sin\theta_i\\
&=ml^2\left((n-i+1)\ddot\theta_i\right.\\
&\qquad\qquad+ (n-i+1)\sum_{k=1}^{i-1}\left(\ddot\theta_k\cos(\theta_i-\theta_k)-\dot\theta_k(\dot\theta_i-\dot\theta_k)\sin(\theta_i-\theta_k)+\dot\theta_i\dot\theta_k\sin(\theta_i-\theta_k)\right)\\
&\qquad\qquad+ \left.\sum_{k=i+1}^n(n-k+1)\left(\ddot\theta_k\cos(\theta_i-\theta_k)-\dot\theta_k(\dot\theta_i-\dot\theta_k)\sin(\theta_i-\theta_k)+\dot\theta_i\dot\theta_k\sin(\theta_i-\theta_k)\right)\right)\\
&\qquad\qquad+ mgl(n-i+1)\sin\theta_i\\
&=ml^2\left((n-i+1)\ddot\theta_i + (n-i+1)\sum_{k=1}^{i-1}\left(\ddot\theta_k\cos(\theta_i-\theta_k)-\dot\theta_k^2\sin(\theta_i-\theta_k)\right)\right.\\
&\qquad\qquad+ \left.\sum_{k=i+1}^n(n-k+1)\left(\ddot\theta_k\cos(\theta_i-\theta_k)-\dot\theta_k^2\sin(\theta_i-\theta_k)\right)\right)\\
&\qquad\qquad+ mgl(n-i+1)\sin\theta_i
\end{align*}
\subsection{Generalization to an Infinite Rope}
e
\end{document}
